
```{r, include = FALSE}
leanbuild::set_knitr_image_path()
```

# Introduction


## Motivation
The [Open Case Studies project](https://www.opencasestudies.org), developed at the [Johns Hopkins Data Science Lab](https://jhudatascience.org/), is an education platform that provides self-contained, multimodal, peer-reviewed, and open-source guides for real-world examples for active experiences of complete data analyses. The intention of this guide is to provide instructors more information about how to make the most of our case studies.


## Target Audience  

This guide is intended for educators who are interested in using the Open Case Studies for instruction.

Elements of the Case studies can be helpful for instructors who teach:

- High school students
- Undergraduate students
- Graduate students

Elements of the case studies  can assist with teaching courses about the following topics:

- Data science
- Statistics
- Public health
- Programming
- Technical writing  

... and more

## Curriculum  

This guide documents:

- The open case studies philosphy
- Various entry points to using the case studies (including an R package to enable modular use of the case studies)
- Examples of how to use the case studies
- How to modify and adapt components of the case studies for the classroom
- How to contribute new case studies. 


## Open Case Studies Philosophy

```{r, fig.align='center', echo = FALSE, fig.alt= "Open Case Study Graphic"}
leanbuild::include_slide("https://docs.google.com/presentation/d/17DhSo5YTKzP9bl-zfduezsyfItZRzJYmIgczUvr-Cw0/edit#slide=id.g107fd794960_0_154")
```

## Open Case Studies Anatomy
