
```{r, include = FALSE}
leanbuild::set_knitr_image_path()
```

# Open Case Study Infastructure

## Learning Objectives


## Libraries

For this chapter, we'll need the following packages attached:

*Remember to add [any additional packages you need to your course's own docker image](https://github.com/jhudsl/OTTR_Template/wiki/Using-Docker#starting-a-new-docker-image).

```{r}
library(magrittr)
```

# Topic of Section

You can write all your text in sections like this!

## Subtopic

Here's a subheading and some text in this subsection!

### Code examples

You can demonstrate code like this:

```{r}
output_dir <- file.path("resources", "code_output")
if (!dir.exists(output_dir)) {
  dir.create(output_dir)
}
```



### Image example


How to include a Google slide. It's simplest to use the `leanbuild` package:

```{r, fig.align='center', echo = FALSE, fig.alt= "Major point!! example image"}
leanbuild::include_slide("https://docs.google.com/presentation/d/1YmwKdIy9BeQ3EShgZhvtb3MgR8P6iDX4DfFD65W_gdQ/edit#slide=id.gcc4fbee202_0_141")
```





### Video examples

You can use `knitr::include_url()` like this:

```{r}
knitr::include_url("https://www.youtube.com/embed/VOCYL-FNbr0")
```

OR this works:

<iframe src="https://www.youtube.com/embed/VOCYL-FNbr0" width="672" height="400px"></iframe>

### Links to files

This works:

```{r, fig.align="center", echo=FALSE}
knitr::include_url("https://www.messiah.edu/download/downloads/id/921/Microaggressions_in_the_Classroom.pdf", height = "800px")
```

Or this:

[This works](https://www.messiah.edu/download/downloads/id/921/Microaggressions_in_the_Classroom.pdf).

Or this:

<iframe src="https://www.messiah.edu/download/downloads/id/921/Microaggressions_in_the_Classroom.pdf" width="672" height="800px"></iframe>

### Links to websites

Examples of including a website link.

This works:

```{r, fig.align="center"}
knitr::include_url("https://yihui.org")
```

OR this:

![Another link](https://yihui.org)

OR this:

<iframe src="https://yihui.org" width="672" height="400px"></iframe>

### Citation examples

We can put citations at the end of a sentence like this [@rmarkdown2021].
Or multiple citations [@rmarkdown2021, @Xie2018].

but they need a ; separator [@rmarkdown2021; @Xie2018].

In text, we can put citations like this @rmarkdown2021.

## Print out session info

```{r}
sessionInfo()
```
