
```{r, include = FALSE}
ottr::set_knitr_image_path()
```

# Modifying and creating open case studies

## Learning Objectives

This chapter will cover how to modify the case studies to your own needs using the following methods:  

- Modular case study use with the help of the [OCSdata package](https://github.com/opencasestudies/OCSdata)
- Modifying a case study with [GitHub](https://github.com/opencasestudies) and [RStudio](https://www.rstudio.com/)
- Creating your own case study with our [template](https://github.com/opencasestudies/ocs-bp-template) and [MakeCaseStudies](https://rsconnect.biostat.jhsph.edu/MakeCaseStudies/)

## Modular use

Some educators may find that only certain sections of a case study are relevant to their specific needs. For example, a statistics teacher may want students to practice the skills covered in the data analysis section, but doesn't have time to go through the whole case study. The case studies are designed to allow for such use. This educator and their students may jump right in to any case study section without working through any previous sections. This is made possible becase the data files are saved at the end of each section. These data files are made available on the case study's GitHub repository and may also be downloaded with the help of the OCSdata package. See Chapter 2 for more details on the structure and organization of a case study data folder. The table below explains which data sub-folder and package function to use for each case study section. 

| Data Folder | Case Study Section | OCSdata Function | 
| ----- | -------- | ------ |
| raw | Data Import | `raw_data` | 
| imported | Data Exploration, Data Wrangling | `imported_data` |
| wrangled | Data Visualization, Data Analysis | `wrangled_csv`, `wrangled_rda` |
| simpler_import | Data Import | `simpler_import_data` | 
| extra | Suggested Homework (?) | `extra_data` |

*step by step example of how to jump into the middle of a case study (do data analysis section as an example?)

## Modify a case study

*short explanation of case study structure: RStudio projects written in Rmd, knitted to HTML and hosted on GitHub
*tutorial on .Rmd and knitting in RStudio
*tutorial on GitHub: forking
*step by step example of forking a case study repository, editing Rmd content, knitting, and sharing the output

## Create a case study

*tutorial on how to create a case study using GitHub template
*tutorial on how to create a case study using [MakeCaseStudies](https://rsconnect.biostat.jhsph.edu/MakeCaseStudies/) app

## Session info

```{r, echo = FALSE}
sessionInfo()
```
