
```{r, include = FALSE}
ottr::set_knitr_image_path()
```

# Modifying and creating open case studies

## Learning Objectives

This chapter will cover how to modify the case studies to your own needs using the following methods:  

- Modular case study use with the help of the [OCSdata package](https://github.com/opencasestudies/OCSdata)
- Modifying a case study with [GitHub](https://github.com/opencasestudies) and [RStudio](https://www.rstudio.com/)
- Creating your own case study with our [template](https://github.com/opencasestudies/ocs-bp-template) and [MakeCaseStudies](https://rsconnect.biostat.jhsph.edu/MakeCaseStudies/)

## Libraries

For this chapter, we'll need the following packages attached:

```{r}
library(OCSdata)
```

## Modular use

*short explanation of how case studies can be used modularly for those who want to break the case study up or are only interested in part of the case study 
*table about which package functions to use for each section in a case study you could start from
*step by step example of how to jump into the middle of a case study (do data analysis section as an example?)

## Modify a case study

*short explanation of case study structure: RStudio projects written in Rmd, knitted to HTML and hosted on GitHub
*tutorial on .Rmd and knitting in RStudio
*tutorial on GitHub: forking
*step by step example of forking a case study repository, editing Rmd content, knitting, and sharing the output

## Create a case study

*tutorial on how to create a case study using GitHub template
*tutorial on how to create a case study using MakeCaseStudies app

## Session info

```{r, echo = FALSE}
sessionInfo()
```
